Exposing Disputed Statements on the Web

### 2009-03-27 papers/uist_thinklink/thinklink_changes_beth.tex
Starting to implement Mayur-suggested changes. Distinguishing more clearly between topic and claim. Adding icons to headers.

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

@@

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed on presents only one side of a contentious issue. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.

All information in Think Link is provided by users. Think Link is designed to cator to two usage scenarios. Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with. Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.

@@

The web contains a huge amount of information, but but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to gain a broad understanding ofa topic then they will need to either stick to sources that they trust or spend time looking for information on other web sites that conflicts with what they have read. Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.

In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view. When Think Link is used as a browser plugin it will highlight text that makes a disputed claim. If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by the voting of other Think Link users (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two distinct groups of people. Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them. Sceptical readers install Think Link as a browser plugin so that they can see when things they read are disputed and find other links that present other points of view. A reader may be an activist for one issue and a sceptical reader for others.

@@

The design of Think Link was guided by two user studies, in which we observed the behavior of users as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on work in several different areas. The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}. The model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}. The idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.

@@

Prior IBIS tools have been intended for conflict modelling and resolution: users build up a complex graph modelling an issue and then use this graph to decide what to do. By contrast Think Link uses an IBIS graph for conflict discovery and evidence identification. In a tool like gIBIS a user is encouraged to break down their argument into as much detail as possible and encouraged to use the graph itself to reach a decision. By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form their opinion primarily by reading the articles that have been linked as evidence. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit the expected usage for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} is perhaps the IBIS tool most similar to Think Link. Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses. While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways. In Cohere, a user attaches a web snippet to their idea in order to use it as evidence. By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument. More generally,

More generally, a key way Think Link differs from Cohere is that it separates the creation of claims from their association with snippets. A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.

@@

When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use. For Think Link, we tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model. The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not. FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. Think Link's database automatically imports all contentious claims identified by Snopes.

@@

Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors. Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g. people from a company editing pages about that company).

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

Think Link is designed to be used in two different ways. Sceptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites. Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with. The same user may act as a sceptical reader sometimes and an activist at other times.

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).

@@

In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

We found that it was important to allow the claim browser interface to be used in two different ways. When a user is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are four types of node: snippets, claims, topics, and users. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A claim can support,oppose, or relate-to another claim, a claim can relate-to a topic, and a topic can relate-to another topic. This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.

Think Link uses topics to group together related claims. A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.

@@

Think Link does not require that a user associate a snippet with a snippet at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with. In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

@@

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.

Think Link uses the Wikify! algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.

@@

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.

@@

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain. In future work hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

@@

We performed two qualitative ``think aloud'' user studies. The aim of these studies was to inform the development of Think Link. The studies were not intended to validate the design of Think Link as being correct. Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points. To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the Internet to find information. We recruited participants using a posting to the Craigslist.org classified advert site. In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

@@

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case). The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).

@@

\subsubsection{High-Level Impressions}

Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.

@@

The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet. When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype). There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where what claims are true can change fast. If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.

@@

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics. Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.

@@

We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue. Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors. It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.

>>>>

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}  % beth: conf info year
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

@@

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed or presents only one side of a contentious issue. % beth: typo
As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. 
If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against that snippet's claim. % beth: word changes

Users provide all Think Link's information: they highlight new snippets, and create and relate claims % beth: reworded, added details 
Think Link is designed to cater to two primary usage scenarios. % beth: typo, insert 'primary' 
Activists who care strongly about a particular issue can combine Think Link with a search engine to find and mark where web sites make statements that they disagree with.  % beth: word changes
Skeptical readers can install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints. % beth: word changes

@@

A huge amount of information is available on the web, but some websites have inaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004}, and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.  % beth: reworded
If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust have full information, or spend time searching for information on other web sites that conflicts with what they have read.  % beth: reworded
Even if a user researches every topic they read, they may not look for contradictory evidence for claims they had not realized were disputed. % beth: reworded, but still awkward

In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources with different points of view.  % beth: reworded
When Think Link is used as a browser plugin, it will highlight snippets of text that make disputed claims.  % beth: added 'snippets'
If a user clicks on such a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the snippet's claim.  % beth: shortened, reworded
The best evidence is judged by votes from other Think Link users (Figure~\ref{claimview}).  % beth: new sentence, reworded

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two primary usage scenarios. % beth: insert 'primary' 
Activists who care strongly about a particular issue can combine Think Link with a search engine to find and mark where web sites make statements that they disagree with.  % beth: word changes
Skeptical readers can install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints. % beth: word changes
A reader may be an activist for one issue and a skeptical reader for others.

@@

The design of Think Link was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for the Activist and Skeptical Reader. % beth: typos, reworded

@@

Think Link builds on work in several different areas. 
The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.  % beth: typo
The idea of highlighting potentially untrustworthy information was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}.   % beth: reworded
Tagging systems~\cite{Marlow2006} influenced Think Link's model of using a community to collect and filter information from a range of sources. % beth: reworded
Gathering a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.  % beth: reworded

Think Link is interesting because it combines ideas from these different domains to create a collaborative infrastructure for connecting conflicting information on the web.  % beth: big rewording, not sure if you like it...

@@

Prior IBIS tools have been intended for conflict modeling and resolution: users build a complex graph modeling an issue and then use this graph to make a decision.  % beth: typos, word changes
By contrast, Think Link uses an IBIS graph for conflict discovery and evidence identification.  % beth: comma
In a tool like gIBIS, a user is encouraged to break down their argument into as much detail as possible and to use the graph itself to reach a decision.  % beth: comma, removed word
By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim; the user is expected to form their opinion primarily by reading the articles that have been linked as evidence.  % beth: , and->semicolon
In Think Link it is acceptable for a claim to be not linked to any other claims or topics, but be associated with many snippets --- this would not fit the expected usage for other IBIS tools. % beth: reworded

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.  % beth: what issues?? say a few!
We believe that while the problems they observe are important when an IBIS tool is being used for conflict modeling and resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.  % beth: comma

Cohere~\cite{Shum2008} is the IBIS tool most similar to Think Link.  % beth: removed word
Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from web pages.  % beth: rmeoved words
While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways. In Cohere, a user attaches a web snippet to their idea in order to use it as evidence. 
In Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.  % beth: hmmm... think link really does both use cases

More generally, Think Link's key difference from Cohere is that it separates the creation of claims from their association with snippets.  % beth: reworded
A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.

@@

When choosing an argumentation structure, there is an inherent trade-off between accurately modeling the structure of an argument and making the tool easy to use.  % beth: typo
For Think Link, we tried to minimize the model complexity, and thus adopted a simple pro/con/netural linking model.  % beth: reworded
The goal is to show a user what sources they should look at when forming an argument for or against a claim, rather than to present the detailed logical structure of an argument.  % beth: big rewording

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. 
Snopes is a database of urban legends that the site owners have investigated to determine whether they are true.  % beth: removed words
Think Link's database automatically imports all contentious claims identified by Snopes. % beth: moved sentence up
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.

@@

Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy. WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors. Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g. people from a company editing pages about that company).

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. 
ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are interested in.  % beth: typo
Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

Think Link is designed to be used in two different ways. 
Skeptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites.  % beth: typo
Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of skeptical readers to claims that they disagree with.  % beth: typo
The same user may act as a skeptical reader sometimes and an activist at other times.  % beth: typo

@@

If a skeptical reader has installed the Think Link browser extension, Think Link will draw the user's attention to text snippets that make or imply disputed claims with red highlighting (Figure~\ref{highlight}).  % beth: rewording
If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. Clicking on a highlighted snippet will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).  % beth: reworded

@@

In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. 
To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item. % beth: typo

@@

We found that it was important to allow the claim browser interface to be used in two different ways. 
When a user is browsing a web page and sees a disputed claim, they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail, it is preferable to use a full-window interface, as the small popup interface is too small to easily view large amounts of information.  % beth: reworded

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are four types of node: snippets, claims, topics, and users. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to; a user is a person who uses Think Link.  % beth: typos
Nodes are connected by typed, directed links.  % beth: word changes
There are three link types: supports, opposes, and relates-to. 
A claim can support, oppose, or relate-to another claim.
A claim can also relate-to a topic, and a topic can relate-to another topic.  % beth: new sentence
This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.

Think Link uses topics to group together related claims. 
A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. % beth: typo
Alternatively, it can be what claims are about, for example ``Carbon Dioxide''.  % beth: changed wording
Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.

@@

Think Link does not require that a user associate a snippet with a snippet at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. 
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that the user disagrees with.  % beth: typos
In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

@@

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.  % beth: not clear what happens if they never file them...

Think Link uses the Wikify! algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts which pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.  % beth: typos
Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. 
The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to. % beth: typo

@@

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together. % beth: maybe more here?

@@

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired.  % beth: removed words
In future work we hope to reduce these privacy issues.  % beth: typo
One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

@@

We performed two qualitative ``think aloud'' user studies. The aim of these studies was to inform the development of Think Link. The studies were not intended to validate the design of Think Link as being correct. Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points. To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for. % beth: maybe talk about plans for the larger study? (would that add or take away from this?)

@@

For the first study we recruited twelve paid participants.  % beth: 12->twelve
Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the Internet to find information. We recruited participants using a posting to the Craigslist.org classified advert site. In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

@@

Study sessions took approximately forty-five minutes.  % beth: number
Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited six paid participants.  % beth: number
Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``skeptical reader'' use case). The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).

@@

\subsubsection{High-Level Impressions}  % beth: not sure this section is necessary, or maybe spin it more to be like "yes, people actually said they'd use this""... demonstrating practicality and usefullness

Response was generally positive, with many participants being very keen to use the tool soon. 
One participant said ``I can see myself getting addicted to this'', and several participants asked us to notify them when it is properly deployed.  % beth: typo
Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Most participants in the first study, and all participants in the second study, were able to use the tool competently.  % beth: comma
Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.

@@

The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet. When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype). There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:  % beth: the folloing list should be indented or bulleted or something

@@

Several users got confused by claims that referred to similar events at different points in time. 
For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written.  % beth: typo
This is a particular problem when talking about breaking news events, where which claims are true can change fast.  % beth: word change
If Think Link is to be effective for describing such events then it will need to have better support for identifying the time at which a claim was asserted to be true. % beth: removed words, maybe say we'll work on this in future?  maybe have timeline?

@@

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. 
The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.  % beth: typo
In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).  % beth: removed word
We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics. Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious. % beth: but we will once we launch and do big user study yada yada yada

@@

We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on all sides of the issue.  % beth: word change
Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by web page authors.  % beth: clarified
Users can identify snippets making on web pages that make disputed claims, connect those snippets to the appropriate arguments, and create relationships to claims on other websites.  % beth: big rewording

Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then uses a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph. % beth: reworded
